Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-07-13 paper/submitted/round2_png/algorithms_v4_cmame.tex
small wording/spelling changes

where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively; initially, $\Omega_{LF}=\Omega$. The resulting mixed-fidelity models can be described by,

@@

\Cref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, or be a reduced-order model, or have a reduced parameter and/or state space. The derived error estimate is not applicable to all models, however. It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model. The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$. For example, compared to the high-fidelity model, the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace. The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy. We note that in the case where the two models correspond to two levels of mesh refinement, method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
%, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$. %implied by admissibility of LF to HF

>>>>

where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogeneous Dirichlet boundary conditions. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively; initially, $\Omega_{LF}=\Omega$. The resulting mixed-fidelity models can be described by,

@@

\Cref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena (as in the example above), or be a reduced-order model, or have a reduced parameter and/or state space. The derived error estimate is not applicable to all models, however. It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model. The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$. For example, compared to the high-fidelity model, the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace. The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy. We note that in the case where the two models correspond to two levels of mesh refinement, method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
%, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$. %implied by admissibility of LF to HF

### 2017-07-13 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
small wording/spelling changes

The QoI region is $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The parameters $q$ we wish to infer correspond to the forcing function. The observations are sparse measurements of the state.
\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). We arbitrarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

>>>>

The QoI region is $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The parameters $q$ we wish to infer correspond to the forcing function. The observations are sparse measurements of the state.
\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). We choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%
